make_lineplots_simd_deciles

### 2023-07-12 minos/outcomes/make_lineplots_simd_deciles.Rmd
stupid bugs again

```{python simd deciles, fig.path="plots/"}
# packages need installing in R using py_install("package"). honestly this seems not worth it..
from minos.outcomes.make_lineplots import main as lineplot_main
# define test parameters and run.
directories = "baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline"
tags = "National Average,First,Second,Third,Fourth,Fifth,Sixth,Seventh,Eighth,Ninth,Tenth"
subset_function_strings = "who_alive,who_first_decile,who_second_decile,who_third_decile,who_fourth_decile,who_fifth_decile,who_sixth_decile,who_seventh_decile,who_eigth_decile,who_ninth_decile,who_tenth_decile"
prefix="simd_deciles"
config_mode = "glasgow_scaled"
lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="National Average", v="SF_12", method='nanmean')
```

```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
knitr::include_graphics(here::here("plots", "baseline_all_child_uplift_SF_12_aggs_by_year.pdf"), error=FALSE)
```

>>>>

```{python simd deciles, fig.path="plots/"}
# packages need installing in R using py_install("package"). honestly this seems not worth it..
from minos.outcomes.make_lineplots import main as lineplot_main
# define test parameters and run.
directories = "baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline"
tags = "National Average,First,Second,Third,Fourth,Fifth,Sixth,Seventh,Eighth,Ninth,Tenth"
subset_function_strings = "who_alive,who_first_simd_decile,who_second_simd_decile,who_third_simd_decile,who_fourth_simd_decile,who_fifth_simd_decile,who_sixth_simd_decile,who_seventh_simd_decile,who_eighth_simd_decile,who_ninth_simd_decile,who_tenth_simd_decile"
prefix="simd_deciles"
config_mode = "glasgow_scaled"
lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="National Average", v="SF_12", method='nanmean')
```

```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
knitr::include_graphics(here::here("plots", "simd_deciles_SF_12_aggs_by_year.pdf"), error=FALSE)
```
